Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-10 Paper/paper.tex
Reinforced argument to use border ASes

Today, most such control is exercised at the country level,
as governments have recognized both the threat and the opportunity
that is posed by ubiquitous online communication. For example, much
of the organization, revolutionary momentum, and broadcasting of
events during the Arab Spring have been attributed to social media
communications through the Internet \cite{arabspring}. Several countries
sought to control these movements by disconnecting in-country networks from the rest of the world \todo[inline]{need references here}.

These two factors, increasing levels of content monitoring and
Internet dependence, point to the need for improved tools and methods
for studying worldwide Internet censorship and surveillance over time.
\todo[inline]{A SENTENC OR TWO HERE SUMMARIZING THE STATE OF THE FIELD AND WHAT'S
  MISSING.}  In this paper, we focus on AS-level topology and on
censorship, asking how AS topology has changed over time with respect
to national boundaries.  We define \emph{chokepoint potential} to
quantify how a country’s AS topology is organized in terms of paths
that can carry traffic across international borders.  We developed a
suite of tools, called \toolname, for studying national chokepoints on
the AS graph efficiently. To illustrate these ideas and tools, we
study how chokepoint potential correlates with two independent
measures of civilian liberty, finding \todo[inline]{NEED A RESULT HERE}. \todo[inline]{NEED A
  RESULT FOR WHAT WE FOUND FOR EVOLU- TION OVER TIME}.

@@

@@

% Why Border ASes?
In order to identify AS chokepoints and compare nations, we need a measure that can be calculated from the many paths between
ASes. First, we decided to use a measure that is evaluated only on border ASes, or ASes that lie one hop from an AS belonging to another nation. 
We argue that this is intuitive because border
ASes are the first opportunity for nations to censor incoming traffic and the last opportunity for nations to block access to
foreign websites from within their borders. Additionally, while internal chokepoints may intercept many paths, those paths are required
to have entered through a border AS (in the case of out-to-in paths) or exit through a border AS (for in-to-out paths). This simplification has
the added benefit of making calculations more efficient.

>>>>

Today, most such control is exercised at the country level,
as governments have recognized both the threat and the opportunity
that is posed by ubiquitous online communication. For example, much
of the organization, revolutionary momentum, and broadcasting of
events during the Arab Spring have been attributed to social media
communications through the Internet \cite{arabspring}. Several countries
sought to control these movements by disconnecting in-country networks from the rest of the world \cite{BGPdisrupt}.
These two factors, increasing levels of content monitoring and
Internet dependence, point to the need for improved tools and methods
for studying worldwide Internet censorship and surveillance over time.
\todo[inline]{A SENTENC OR TWO HERE SUMMARIZING THE STATE OF THE FIELD AND WHAT'S
  MISSING.}  In this paper, we focus on AS-level topology and on
censorship, asking how AS topology has changed over time with respect
to national boundaries.  We define \emph{chokepoint potential} to
quantify how a country’s AS topology is organized in terms of paths
that can carry traffic across international borders.  We developed a
suite of tools, called \toolname, for studying national chokepoints on
the AS graph efficiently. To illustrate these ideas and tools, we
study how chokepoint potential correlates with two independent
measures of civilian liberty, finding \todo[inline]{NEED A RESULT HERE}. \todo[inline]{NEED A
  RESULT FOR WHAT WE FOUND FOR EVOLU- TION OVER TIME}.

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{bnodes}
	\caption{The ratio of ASes that are border ASes plotted over several years.}\label{fig:bnodes}
\end{figure}

@@

% Why Border ASes?
In order to identify AS chokepoints and compare nations, we need a measure that can be calculated from the many paths between
ASes. First, we decided to use a measure that is evaluated only on border ASes, or ASes that lie one hop from an AS belonging to another nation. 
The evolution of AS relationships and national boundaries on the AS graph hints that border ASes are an important feature in regards to the flow
of information. Consider that while the number of ASes globally has continued to grow rapidly, the number of border ASes has grown more slowly.
This result is depicted in figure \ref{fig:bnodes}. Additionally, while internal chokepoints may intercept many paths, those paths are required
to have entered through a border AS (in the case of out-to-in paths) or exit through a border AS (for in-to-out paths). This focus on border ASes has
the added benefit of making calculations more efficient.
